Response to reviewers

### 2022-06-07 response/response3.Rmd
figure 7
hgc confusion
unsatisfactory to disappointing
last AE comment

@@

@@

@@

>>>>

We have done as you suggest for the density plots, but feel the back-to-back bar chart is better for the hgc comparison.

@@

Done

@@

We have changed "unsatisfactorily" to "disappointingly"

@@

This bullet list is a path forward. It is clearly not a summary of what was presented. We did not discuss teaching modeling. We simply used one type of model for pre-rpcessing the data to handle unusual observations. No change made.
